---
title: "Data Aggregation"
author: "Edie Espejo"
date: "3/30/2019"
output: pdf_document
---

I just drove myself into a deep dark pit of data terror, but I was able to find one archive from Kaggle using an internet time machine that gave me an old download link that somehow still worked. 159490 businesses intersect between the 2017 data I found and the 2019 data…

## Libraries
```{r, message=FALSE, warning=FALSE}
library(jsonlite)
library(tibble)
library(dplyr)
library(tidyr)
library(stringr)
library(readr)
library(ggplot2)
```


## 2019 Data
I downloaded this straight off of the Yelp Challenge.

```{r, message=FALSE, warning=FALSE}
yelp_2019 <- "../../../data/yelp-2019/business.json"
yelp_2019 <- stream_in(file(yelp_2019))
yelp_2019 <- flatten(yelp_2019)
yelp_2019 <- as_tibble(yelp_2019)
```

## 2017 Data
I used the wayback machine to get me this download link.

```{r, message=FALSE, warning=FALSE}
wayback <- "../../../data/yelp-2017/yelp_business.csv"
wayback <- read_csv(wayback)
head(wayback)
```


## Combining the datasets
I want to get choose to use businesses that are in both the datasets only.

```{r}
intersecting_businesses <- intersect(wayback$business_id, yelp_2019$business_id)
length(intersecting_businesses)
```

Sanity checks... 

```{r}
wayback_subset   <- wayback %>% filter(business_id %in% intersecting_businesses)
yelp_2019_subset <- yelp_2019 %>% filter(business_id %in% intersecting_businesses)
c(nrow(wayback_subset), nrow(yelp_2019_subset))
```

I'm going to just collect the 0's and 1's.

```{r}
yelp_2018_subberset <- yelp_2019_subset %>% select(business_id, is_open) %>% rename(open_2019=is_open)
head(yelp_2018_subberset)
```

```{r}
wayback_subset <- wayback_subset %>% rename(open_2017=is_open)
causal_set <- merge(wayback_subset, yelp_2018_subberset, by="business_id")
# write.csv(causal_set, file="../../../data/causal_set.csv")
head(causal_set)
```

The businesses we look at should have been open in 2017.

```{r}
causal_set <- causal_set[which(causal_set$open_2017==1),]
dim(causal_set)
```

According to this, 6,267 closed in two years. The other 127,561 carried on.

```{r}
table(causal_set$open_2019)
```

```{r, eval=FALSE}
causal_set %>% filter(open_2019==0)
```

```{r}
causal_set_cities <- data.frame(sort(table(causal_set$city), decreasing=TRUE))
names(causal_set_cities) <- c("city", "frequency")
ggplot(head(causal_set_cities, 15), aes(x=city, y=frequency)) + geom_bar(stat="identity") + theme(axis.text.x = element_text(angle = 40, hjust = 1)) + ggtitle("Cities in the dataset")
```


```{r}
closed_businesses <- data.frame(sort(table(causal_set %>% filter(open_2019==0) %>% pull(city)), decreasing=TRUE))
names(closed_businesses) <- c("locations", "frequency")
ggplot(head(closed_businesses, 10), aes(x=locations, y=frequency)) + geom_bar(stat="identity") + theme(axis.text.x = element_text(angle = 40, hjust = 1)) + ggtitle("Areas with Closed Businesses")
```


```{r}
open_businesses <- data.frame(sort(table(causal_set %>% filter(open_2019==1) %>% pull(city)), decreasing=TRUE))
names(open_businesses) <- c("locations", "frequency")
ggplot(head(open_businesses, 10), aes(x=locations, y=frequency)) + geom_bar(stat="identity") + theme(axis.text.x = element_text(angle = 40, hjust = 1)) + ggtitle("Areas with Open Businesses")
```