---
title: "Yelp Data Aggregation"
html_document:
    theme: united
---

I have two Yelp datasets, one from 2017 and the other from 2019.

## Libraries
```{r, message=FALSE, warning=FALSE}
library(jsonlite)
library(tibble)
library(dplyr)
library(tidyr)
library(stringr)
library(readr)
library(ggplot2)
library(lubridate)
```

### Yelp Challenge 2019
```{r, message=FALSE, warning=FALSE}
yelp_2019 <- "../../../data/yelp-2019/business.json"
yelp_2019 <- stream_in(file(yelp_2019))
yelp_2019 <- flatten(yelp_2019)
yelp_2019 <- as_tibble(yelp_2019)
```

### Yelp Challenge 2017
```{r, message=FALSE, warning=FALSE}
wayback <- "../../../data/yelp-2017/yelp_business.csv"
wayback <- read_csv(wayback)
```

```{r}
reviews <- read_csv("../../../data/yelp-2017/yelp_review.csv")
```


### Cutting into subsets on shared businesses only
```{r}
intersecting_businesses <- intersect(wayback$business_id, yelp_2019$business_id)
wayback_subset          <- wayback %>% filter(business_id %in% intersecting_businesses)
yelp_2019_subset        <- yelp_2019 %>% filter(business_id %in% intersecting_businesses)
```

### Take only the 0's and 1's from Yelp Challenge 2019 Business Data
```{r}
yelp_2019_subberset <- yelp_2019_subset %>% 
  select(business_id, is_open) %>% 
  rename(open_2019=is_open)
```

### Merge datasets
```{r}
wayback_subset <- wayback_subset %>% rename(open_2017=is_open)
causal_set     <- merge(wayback_subset, yelp_2019_subberset, by="business_id")

# * ONLY KEEP THOSE THAT WERE OPEN IN 2017
causal_set <- causal_set[which(causal_set$open_2017==1),]
```

### Narrow down to Las Vegas only
```{r}
causal_lv <- causal_set %>% filter(city=="Las Vegas") %>% filter(state=="NV")
causal_lv <- causal_lv %>% select(-city, -state)
```

### Removal of no address
```{r}
no_addy   <- which(sapply(causal_lv %>% select(address), nchar)<10)
causal_lv <- causal_lv[-no_addy,]
```

### Filtering for food and restaurants, removing groceries
```{r}
causal_lv <- causal_lv %>% 
  filter(grepl("Restaurants|Food", categories)) %>% 
  filter(!grepl("Grocery", categories))
```

```{r}
causal_lv <- causal_lv %>% 
  filter(!grepl("Walgreens", name)) %>%
  filter(!grepl("Specialty Food", categories)) %>%
  filter(!grepl("Convenience Stores", categories)) %>%
  filter(!grepl("Gas Stations", categories)) %>%
  filter(!grepl("Car Wash", categories)) %>%
  filter(!grepl("Wine & Spirits", categories)) %>%
  filter(!grepl("Festival", categories)) %>%
  filter(!grepl("Water Store", categories))
```

```{r}
# create binary variable for type of restaurant (American vs. not)
causal_lv <- causal_lv %>% 
  mutate(american = ifelse(grepl("American|Burgers|Steak", categories), "1", "0"))
```


### Calculating age
```{r}
# * GET ID'S TO MATCH TO REVIEWS
lv_business_id <- causal_lv %>% pull(business_id)

lv_reviews <- reviews %>% filter(business_id %in% lv_business_id)

min_dates <- sapply(1:length(lv_business_id), function(ix) {
  id <- lv_business_id[ix]
  min_date <- lv_reviews %>% filter(business_id==id) %>% 
    summarize(min_date=min(as.Date(date))) %>% 
    mutate(min_date=as.character(min_date)) %>% 
    pull(min_date)
  min_date
})

earliest_review <- data.frame(cbind(lv_business_id, min_dates)) %>%
  rename(business_id=lv_business_id, age=min_dates)

causal_lv <- inner_join(causal_lv, earliest_review, by="business_id")
causal_lv <- causal_lv %>% 
  mutate(age=int_length(interval(start=age, end=today()))/60/60/24)
head(causal_lv %>% select(age))
```

### Identifying multiples/chains
```{r}
causal_lv <- causal_lv %>% 
  mutate(chain=gsub("'|-", "", tolower(name))) %>% 
  mutate(chain=duplicated(chain))
```

### Remove open 2017
```{r}
causal_lv <- causal_lv %>% select(-open_2017, -latitude, -longitude)
```

### Write the csv
```{r}
# head(causal_lv)
# write.csv(x=causal_lv, file="../../data/las-vegas-yelp.csv")
```